|

### 2023-01-31 paper.Rmd
autogit

Suprisingly, even after correcting the runtime for both DAE-GP results by removing the time spend during sampling, my implementation of pre-training for DAE-GP still on average takes more time to finish the search process as shown in figure \@ref(fig:airfoil-runtime-noSampling-total). While traditional DAE-GP has a median runtime of `r format(REG_TIME_NOSAMLING, scientific=F)`, s

@@

<!-- REG_TIME_NOSAMLING <-  3550.276852743067 -->
<!-- PT_TIME_NOSAMPLING  <- 8705.007590330817 -->
<!-- PT_TIME_NOSAMPLING_NOPT  <- 6622.027293765 -->

>>>>

Suprisingly, even after correcting the runtime for both DAE-GP results by removing the time spend during sampling, my implementation of pre-training for DAE-GP still on average takes more time to finish the search process as shown in figure \@ref(fig:airfoil-runtime-noSampling-total). While traditional DAE-GP has a median runtime without sampling time of `r format(REG_TIME_NOSAMLING, scientific=F)` seconds , the runtime of pre-trained DAE-GP, without time for samling and pre-training, still increases by a factor of `r round(PT_TIME_NOSAMPLING_NOPT / REG_TIME_NOSAMLING, 3)` to `r format(PT_TIME_NOSAMPLING_NOPT, scientific=F)` seconds.

@@

### 2023-01-31 paper.tex
autogit

To investigate the strong negative impact of pre-training on DAE-GP runtime, I first studied the influence of pre-training on the median number of training epochs that had to be spend at each generation for the training of the DAE-LSTM models \(M_g\). Figure \ref{fig:airfoil-trainingEpochs} shows that pre-training, as expected, strongly reduces the number of training epochs that had to be executed at each generation until the termination condition was reached. While regular DAE-GP trains for a median of 122 epochs at each generation, pre-training reduces the number of median training epochs by a factor of 0.439 to 53.5

@@

If we look at another time consuming operation in DAE-GP, the creation of new individuals by sampling the DAE-LSTM model \(M_G\), we see one main reason for the large runtime increase by pre-training DAE-GP. Figure \ref{fig:airfoil-SamplingTime} shows the median sampling time spend during each generation of the search and it clearly demonstrates that pre-training does strongly increase the time spent on model sampling in comparison to regular DAE-GP. The median time spend on sampling new individual for regular DAE-GP increases by a factor of 6.83 from 29.05581 to 198.4503.

@@

>>>>

To investigate the strong negative impact of pre-training on DAE-GP runtime, I first studied the influence of pre-training on the median number of training epochs that had to be spend at each generation for the training of the DAE-LSTM models \(M_g\). Figure \ref{fig:airfoil-trainingEpochs} shows that pre-training, as expected, strongly reduces the number of training epochs that had to be executed at each generation until the termination condition was reached. While regular DAE-GP trains for a median of 122 epochs at each generation, pre-training reduces the number of median training epochs by a factor of 0.439 to 53.5 training epochs.

@@

If we look at another time consuming operation in DAE-GP, the creation of new individuals by sampling the DAE-LSTM model \(M_G\), we see one main reason for the large runtime increase by pre-training DAE-GP. Figure \ref{fig:airfoil-SamplingTime} shows the median sampling time spend during each generation of the search and it clearly demonstrates that pre-training does strongly increase the time spent on model sampling in comparison to regular DAE-GP. The median time spend on sampling new individual for regular DAE-GP increases by a factor of 6.83 from 29.05581 seconds to 198.4503 seconds.

@@

Suprisingly, even after correcting the runtime for both DAE-GP results by removing the time spend during sampling, my implementation of pre-training for DAE-GP still on average takes more time to finish the search process as shown in figure \ref{fig:airfoil-runtime-noSampling-total}. While traditional DAE-GP has a median runtime without sampling time of 3550.277 seconds , the runtime of pre-trained DAE-GP, without time for samling and pre-training, still increases by a factor of 1.865 to 6622.027 seconds.
